Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}

### 2020-01-18 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
CAV 2020 paper update

%-----------------------------------------------------------
\section{BACKGROUND}
\label{sec:AutomatedVerification}
%-----------------------------------------------------------
%In this section, we present our theory and methodology to obtain the optimal sizing of stand-alone solar PV systems through program synthesis. In particular, 
Fig.~\ref{fig:optimization} illustrates how to obtain the optimal sizing of a stand-alone PV system using the traditional techniques (manual and simulation) and the proposed automated synthesis techniques. Note that the input information is the same for all the methods: weather data, price information, design requirements, as load curve and power demand, and design assumptions). For the automated synthesis, we also define the bound $k$ to restrict the design-space search \textcolor{red}{What are the implications to set this bound?}. 
%
\begin{figure}[h]
\includegraphics[width=0.8\textwidth]{optimalsizingprocess3}
\centering
\caption{Comparison of optimal sizing methods.}
\label{fig:optimization}
\end{figure}

@@

\textcolor{red}{what is the input and output of this algorithm?}

 \begin{algorithm}
 \caption{Synthesis algorithm}
 \begin{algorithmic}[1]
 \begin{scriptsize}
 \renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
  \STATE Initialize variables \\
  \STATE Declare list of PV panels, controllers, batteries, and inverters data and cost \\
%  \STATE Declare list of controllers data and cost \\
%  \STATE Declare list of batteries data and cost \\
%  \STATE Declare list of inverters data and cost \\
  \STATE Declare the maximum possible cost $MaxCost$  \\
  \STATE Declare power demand, power peak, energy consumption \\
  \STATE Declare battery autonomy, depth of discharge, AC voltage \\
  \FOR {$HintCost=0$ to $MaxCost$}
 	\STATE Declare non-deterministic variable to select PV Panel from list \\
 	\STATE Declare non-deterministic variable to select Controller from list \\
 	\STATE Declare non-deterministic variable to select Battery from list \\
 	\STATE Declare non-deterministic variable to select Inverter from list \\ 	
 	\STATE Calculate $E_{corrected}, \, E_{p} $ \\
	\STATE Calculate $N_{TPmin}, \, N_{PSmin}, N_{PPmin} $ \\
 	\STATE Calculate $C_{bank}$ \\
	\STATE Calculate $N_{BS}min, \, N_{BP}min, \, N_{B}total$ \\
	\STATE Requirement enforced by \textbf{assume}$(V_{c})$ \\
 	\STATE Calculate $I_{sc,amb}$ \\
 	\STATE Calculate $I_{c,min}$ \\
 	\STATE Requirement enforced by \textbf{assume}$(I_{c} \wedge V_{in}DC \wedge V_{out}AC)$ \\
%	\STATE Requirement enforced by \textbf{assume}$(V_{in}DC \wedge V_{out}AC )$ \\
%	\STATE Requirement enforced by \textbf{assume}$(V_{out}AC)$ \\
	\STATE Requirement enforced by \textbf{assume}$(Demand \wedge P_{surge})$ \\
%	\STATE Requirement enforced by \textbf{assume}$(P_{surge})$ \\
	\STATE non-deterministic variables hold feasible equipment and cost  \\
	\STATE $F_{obj} \leftarrow  N_{TP}*Panel_{Cost} \, + \, N_{TB}*Battery_{Cost} \, + Controller_{Cost} \, + \, Inverter_{Cost}$ \\
	\STATE Violation check with \textbf{assert}$(F_{obj} > HintCost)$ \\
  \ENDFOR
 \RETURN $(\,)$ 
  \end{scriptsize}
 \end{algorithmic} 
 \label{alg:verification-algorithm}
 \end{algorithm}

@@

\textcolor{red}{proof of correctness? complexity analysis?}

%Note that the process described here in completely automated and that a validation is performed by our {\sc Verify} phase to ensure that the approach is sound.
%---------------------------------------------------------------------------
\section{Results and Discussion}
%---------------------------------------------------------------------------

@@

\noindent \textbf{Simulation Tool and Assumptions.} Related to off-the-shelf simulation tools, only HOMER Pro performs off-grid system with battery backup analysis and includes economical analysis. Therefore, in this study, HOMER Pro will be the simulation tool used to comparison. HOMER Pro: (a) is available only for Microsoft Windows and its annual standard subscription costs US\$ $504.00$~\cite{HOMER}; (b) it does not have the LCC cost in its reports. But it was possible to obtain LCC from the Net Present Cost (NPC) presented by HOMER Pro; (c) the optimization analysis of HOMER allows us to define a load curve and temperature according to data collected from online databases. However, in order to allow a correct comparison, the curve load and the temperature were defined the same as automated synthesis tools; (d) it does not have a explicit equipment called a charge controller. It uses a controller resource that can perform in two different ways, according to the optimization choice or the user choice: ``load-following'' or ``cycle charging''~\cite{HOMER}. During the tests, it was chosen the ``load-following'' controller: it produces only enough power to meet the demand~\cite{HOMER}; (e) It was assumed the value of 5\% of capacity shortage that is equivalent to 95\% of availability of the PV system. By definition, availability is the percentage of time at which a power system is capable of meeting the load requirements~\cite{Khatib2014}. For critical loads, 99\% is considered acceptable. \textcolor{red}{This sentence is hard to understand... could you please break into smaller sentences? While in an ordinary house electrical load, 95\% is considered acceptable; (f) it was assumed a string of two batteries in order to match the voltage of the system of $24$ V DC that was used for the automated synthesis tool; (g) the premise adopted when using HOMER Pro it was that the user does not know the optimal solution and that in order to obtain this solution is necessary to include (at the design phase of the tool) generic PV and batteries modules that HOMER will search for the optimized power of each component}. With that in mind, it was included a generic flat-plate PV of $1$ kW and generic lead-acid batteries of $1$ kW as well (and with capacity of $83.4$ Ah according to HOMER Pro modeling). HOMER, during run-time, decides the size in kW of each module, based on feasibility and lower cost.

@@

In general, the size of the PV panels and battery bank were bigger in HOMER Pro than with the formal synthesis approach, and that discrepancy is not easy to address without some real systems validation. \textcolor{red}{This sentence is hard to understand... try to break into smaller sentences...Just to compare the results obtained from the optimization with the real-world, the authors had four PV systems deployed and monitored since June $2018$ in a riverside community in the Amazonas State in Brazil, with similar demands presented by case studies $1$, $4$, $5$, and $6$, always with a $3$ $\times$ $325$ W ($3$S) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries.} These solutions are more close to the result presented by the proposed formal synthesis approach than HOMER Pro, thereby showing that the solution is sound, which answers \textit{EQ1}.

>>>>

%-----------------------------------------------------------
\section{BACKGROUND}
\label{sec:AutomatedVerification}
%-----------------------------------------------------------
%In this section, we present our theory and methodology to obtain the optimal sizing of stand-alone solar PV systems through program synthesis. In particular, 
Fig.~\ref{fig:optimization} illustrates how to obtain the optimal sizing of a stand-alone PV system using the traditional techniques (manual and simulation) and the proposed automated synthesis techniques. Note that the input information is the same for all the methods: weather data, price information, design requirements, as load curve and power demand, and design assumptions). For the automated synthesis, we also define the bound $k$ to restrict the design-space search. \textcolor{red}{Limiting the length of $k$ we are reducing the time to solve the problem. In one hand, if $k$ is too small, maybe the approach cannot return a solution; in the other hand, it is possible that a solution cannot be found even with an infinite $k$. Therefore, the proper choice of $k$ is important to this method}. 
%
\begin{figure}[h]
\includegraphics[width=0.8\textwidth]{optimalsizingprocess3}
\centering
\caption{Comparison of optimal sizing methods.}
\label{fig:optimization}
\end{figure}

@@

 \begin{algorithm}
 \caption{Synthesis algorithm}
 \begin{algorithmic}[1]
 \begin{scriptsize}
 \renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
   \REQUIRE \textcolor{red}{weather data (temperature, solar irradiance), list of equipment (data sheet and price information), design requirements (load curve, peak demand, output voltage, battery autonomy), design assumptions (battery state of charge, criteria and objectives for technical and cost analysis)}
 \ENSURE \textcolor{red}{FAIL with counter-example showing the optimal sizing; SUCCESS, saying that the project has no feasible solution considering the requirements and the list of equipment available}
  \STATE Initialize variables \\
  \STATE Declare list of PV panels, controllers, batteries, and inverters data and cost \\
%  \STATE Declare list of controllers data and cost \\
%  \STATE Declare list of batteries data and cost \\
%  \STATE Declare list of inverters data and cost \\
  \STATE Declare the maximum possible cost $MaxCost$  \\
  \STATE Declare power demand, power peak, energy consumption \\
  \STATE Declare battery autonomy, depth of discharge, AC voltage \\
  \FOR {$HintCost=0$ to $MaxCost$}
 	\STATE Declare non-deterministic variable to select PV Panel from list \\
 	\STATE Declare non-deterministic variable to select Controller from list \\
 	\STATE Declare non-deterministic variable to select Battery from list \\
 	\STATE Declare non-deterministic variable to select Inverter from list \\ 	
 	\STATE Calculate $E_{corrected}, \, E_{p} $ \\
	\STATE Calculate $N_{TPmin}, \, N_{PSmin}, N_{PPmin} $ \\
 	\STATE Calculate $C_{bank}$ \\
	\STATE Calculate $N_{BS}min, \, N_{BP}min, \, N_{B}total$ \\
	\STATE Requirement enforced by \textbf{assume}$(V_{c})$ \\
 	\STATE Calculate $I_{sc,amb}$ \\
 	\STATE Calculate $I_{c,min}$ \\
 	\STATE Requirement enforced by \textbf{assume}$(I_{c} \wedge V_{in}DC \wedge V_{out}AC)$ \\
%	\STATE Requirement enforced by \textbf{assume}$(V_{in}DC \wedge V_{out}AC )$ \\
%	\STATE Requirement enforced by \textbf{assume}$(V_{out}AC)$ \\
	\STATE Requirement enforced by \textbf{assume}$(Demand \wedge P_{surge})$ \\
%	\STATE Requirement enforced by \textbf{assume}$(P_{surge})$ \\
	\STATE non-deterministic variables hold feasible equipment and cost  \\
	\STATE $F_{obj} \leftarrow  N_{TP}*Panel_{Cost} \, + \, N_{TB}*Battery_{Cost} \, + Controller_{Cost} \, + \, Inverter_{Cost}$ \\
	\STATE Violation check with \textbf{assert}$(F_{obj} > HintCost)$ \\
  \ENDFOR
 \RETURN $(\,)$ 
  \end{scriptsize}
 \end{algorithmic} 
 \label{alg:verification-algorithm}
 \end{algorithm}

@@

\textcolor{red}{(proof of correctness? complexity analysis?)
Note that the process described here in completely automated and that a validation is performed by our {\sc Verify} phase to ensure that the approach is sound.}
%---------------------------------------------------------------------------
\section{Results and Discussion}
%---------------------------------------------------------------------------

@@

\noindent \textbf{Simulation Tool and Assumptions.} Related to off-the-shelf simulation tools, only HOMER Pro performs off-grid system with battery backup analysis and includes economical analysis. Therefore, in this study, HOMER Pro will be the simulation tool used to comparison. HOMER Pro:

\textcolor{red}{reescrevi os itens todos, para tornar a leitura mais tranquila}
\begin{itemize}
\item is available only for Microsoft Windows and its annual standard subscription costs US\$ $504.00$~\cite{HOMER}; 
\item it does not have LCC cost in its reports, only Net Present Cost (NPC). But it was possible to obtain LCC from NPC; 
\item the optimization analysis of HOMER allows us to define a load curve and temperature according to data collected from online databases. However, in order to allow a correct comparison, the curve load and the temperature were defined the same as automated synthesis tools; 
\item it does not have a explicit equipment called a charge controller. During the tests, it was chosen the ``load-following'' option which produces only enough power to meet the demand~\cite{HOMER} and (usually) presents a not overestimated solution; 
\item it was assumed the value of 95\% for the availability of the PV system. By definition, 'availability' is the percentage of time at which a power system is capable of feed the load requirements~\cite{Khatib2014}. For ordinary house electrical load, 95\% is considered acceptable;
\item it was assumed a string of two batteries in order to match the voltage of the system of $24$ V DC that was used for the automated synthesis tool; 
\item it was included a generic flat-plate PV of $1$ kW and generic lead-acid batteries of $1$ kW as well (and with capacity of $83.4$ Ah according to HOMER Pro modeling). HOMER, during run-time, decides the size in kW of each module, based on feasibility and lower cost.
\end{itemize}

@@

\textcolor{red}{In general, the size of the PV panels and battery bank were larger in HOMER Pro than with our formal synthesis approach. Just to compare the results obtained from the optimization with the real-world, the authors had four PV systems deployed and monitored since June $2018$ in a riverside community in the Amazonas State in Brazil, with similar demands presented by case studies $1$, $4$, $5$, and $6$, always with a $3$ $\times$ $325$ W ($3$S) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries.} These solutions are more close to the result presented by the proposed formal synthesis approach than HOMER Pro, thereby showing that the solution is sound, which answers \textit{EQ1}.}
